Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex

The fourth (and last) set of benchmarks considers the following description
for the plant $G_{4}(s)$, which is typically used for evaluating stability
margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}
%
\begin{equation}
\label{exampleA}
G_{4}(s)=\frac{s-1}{s^{2}-s-2}
\end{equation}
%
\noindent where $G_{4}(z)$ is obtained using the ZOH discretisation defined 
in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
seconds).

>>>>

The fourth (and last) set of benchmarks considers the following description
for the plant $G_{4}(s)$, which is typically used for evaluating stability
margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}
%
\begin{equation}
\label{exampleA}
G_{4}(s)=\frac{s-1}{s^{2}-s-2}
\end{equation}
%
\noindent where $G_{4}(z)$ is obtained using the ZOH discretisation defined 
in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
seconds) respectively, as follows
%
\begin{equation}
\label{exampleA-sampletime1}
G_{4a}(z)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
\end{equation}
%
%
\begin{equation}
\label{exampleA-sampletime2}
G_{4b}(z)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
\end{equation}
%
%
\begin{equation}
\label{exampleA-sampletime3}
G_{4c}(z)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
\end{equation}
